greta.Rmd

### 2019-08-08 notebook/may-outbreak-ghost-2.Rmd
with worse initial belief

```{r}
possible_a <- seq(.25, .34, by = 0.005)
true_a <- 0.27   ## reality has just a transient.  use  0.277 for stronger ghost
believe_a <- 0.29 ## believe there's an attractor
true_i <- which.min(abs(possible_a - true_a))
```

@@

```{r}
prior <- dnorm(possible_a, believe_a, 0.01)
prior <- prior / sum(prior)
```

>>>>

```{r}
possible_a <- seq(.25, .34, by = 0.005)
true_a <- 0.27   ## reality has just a transient.  use  0.277 for stronger ghost
believe_a <- 0.31 ## believe there's a strong attractor
true_i <- which.min(abs(possible_a - true_a))
```

@@

```{r}
prior <- dnorm(possible_a, believe_a, 0.05)
prior <- prior / sum(prior)
```
